Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 analysis.tex
added tool description

We implemented the qSKOS tool that can be used for computing the quality checking functions introduced in \ref{sec:criteria} and made it publicly available\footnote{\url{https://github.com/cmader/qSKOS/}}. All data in the Tables \ref{tab:vocs} and \ref{tab:results} have been obtained by utilizing this tool. However, qSKOS is not only capable of returning numeric values, but can also provide a detailed report listing all resources returned by the quality checking functions alongside with the potential cause of the issue.

@@

>>>>

With qSKOS\footnote{\url{https://github.com/cmader/qSKOS/}}, we provide a reference implementation of the previously introduced quality checking functions and a freely-available open source tool for assessing the quality of a given SKOS vocabulary and finding possible quality issues. Users can run the tool by passing a vocabulary and selecting the quality checking functions they want to perform. As a result, they obtain detailed reports listing possibly affected resources alongside with the potential cause of the issue. qSKOS is implemented in Java and can be used as standalone command-line tool or API in any other application. Its design is open for the introduction of additional quality functions.

@@

Results have been generated by using the qSKOS tool against the previously
